D-Hammer: Efficient Equational Reasoning for Labelled Dirac Notation

### 2025-04-08 05tool_eval.tex
.

\section{Implementation and Case Study}
We present \textbf{D-Hammer}, an open-source and publicly
available\footnote{https://github.com/LucianoXu/D-Hammer} implementaion of our
approach.  \textbf{D-Hammer} is an equational prover for Labelled
Dirac notation written in \CC.  It features a parser built using
ANTLR4, and scalar reasoning is powered by the Mathematica
Engine. Users can use commands to make definitions and assumptions in
the maintained context, conduct the normalization and equivalence
checking, and obtain the rewriting trace output.  D-Hammer can be run
interactively from the command line or integrated into other
\CC\ projects as a library.

>>>>

\section{Implementation and Case Study}
We present \textbf{D-Hammer}, an open-source
% and publicly available\footnote{https://github.com/LucianoXu/D-Hammer}
implementation of our approach\footnote{The toll will be made publicly
available in the final version of the paper}.  \textbf{D-Hammer} is an
equational prover for Labelled Dirac notation written in \CC.  It
features a parser built using ANTLR4, and scalar reasoning is powered
by the Mathematica Engine. Users can use commands to make definitions
and assumptions in the maintained context, conduct the normalization
and equivalence checking, and obtain the rewriting trace output.
D-Hammer can be run interactively from the command line or integrated
into other \CC\ projects as a library.
